The Feasibility of Stylometry as a Service

### 2013-12-08 paper/paper.tex
Added architecture qualities.

>>>>

This design is sufficient for Anonymouth in its current form.  As a
desktop appliccation, the user can anonymize her and the document
locally without any additional attack vectors.

\subsection{Requirements for Web Service}

The architecture for a web service imposes different requirements on
an application.  First and foremost, since Anonymouth is a privacy
enhancing technology, the web service \emph{must} not degrade the
privacy protection of the application.  This is a challenge when
migrating from a desktop to web service since the desktop application
does not use any networked communicaiton.  However, there is little
benefit to using Anonymouth on the web if it compromises one's
privacy.

\subsubsection{Low-latency.}
The web service should be near-real-time, i.e. low-latency.  We don't
specify a time requirement but the response should be in the order of
milliseconds to seconds.  A high latency system would not be well
suited for a web service.  An example high latency system could simply
entail sending an encrypted email to a third party who uses Anonymouth
locally and returns the encrypted result.  While this high-latency
system seems trivial, note that a naive implementation will reduce the
user's privacy.  For example, email is very subject to traffic
analysis (CITE) and encrypted email is easy to detect (CITE),
therefore this act alone would raise suspiction.  If this third party
was offering a high-latency anonymiziation service for numerous
people, the network graph would be easy to detect.

\subsection{Architecture Qualities}
There are several qualities of a system architecture that are
considers foundational (CITE lem bass).  These are: availability,
interoperability, modifiability, performance, security, testability,
and usability.  In additional we add privacy as an architecture
quality in our review.

Availability is the measure of the measure of the accesibility and
realibility of the system, e.g. how well does it handle errors.
Interoperability refers to the degree with which a system can interact
with its components or other systems.  Modifiability is important for
large systems so that they can be easily maintained and scale.  The
response of the system to input is its performance.  Security is the
review of a system's ability to protect sensitive data and prevent
unautorized and undesired behaviour.  Testability is an important
factor not only in development but also in a deployed system to ensure
that the system is working as designed.  Usability is notoriously bad
for security software (CITE How Johnny) and refers to the interaction
design.  Lastly, by privacy we mean how well a user's anonymitity is
protected.

In the following sections, we provide an analysis of each quality and
define the requirements for a stylometric web service.

\subsubsection{Availability.}

If the user can not access the web service, then the user is in the
same situation as having a device that can not run Anonymouth
locally.  The entry point to the web service requires a web server.
Realistically, this service will never see the traffic that FaceBook
or Twitter experiences, but the web server should be handle thousands
of requests per day.

A common attack to block availability is a Denial-of-Service (DoS)
attack.  A DoS attack is akin to receiving a momentarily burst in
traffic, i.e. the ``Slashdot effect.''  The difference lies in the
motivation for the sudden attention.  Thus, a service that is
resistant to DoS attacks also scales well to large second-derivative
increases in traffic.

There are many implemenation details to achieve availability that are
beyond the scope of this paper.  We attest that a stylometric service
needs to be available and should consider the effects of sudden
traffic increases.

\subsubsection{Interoperability.}

\subsubsection{Modifiability.}

\subsubsection{Performance.}

\subsubsection{Security.}

\subsubsection{Testability.}

\subsubsection{Usability.}

\subsubsection{Privacy.}
